A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-07 survey.tex
Added the bot opening analysis

@@

However, there are many other problems for which this is not the case. For example, there is no current StarCraft bot that can come up with its own tactical moves, such as ``unit drops''. Some bots do drops, but only if this is hard-coded; no bot has the capability of reasoning about the current situation, synthesize a tactical move that involves a ``unit drop'', and determine that this move is the best one in the current situation. This is related to the lack of real-time adversarial planning techniques that scale up to the size required for RTS games. Similarly, current bots do not exhibit adaptation to opponent strategies. Some switch between different build-orders, but do not fully adapt their strategy. No bot is capable of observing the opponent and autonomously synthesize a good plan from scratch to counter the opponent strategy.

@@

\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{jim.jpg}}]{Jim Raynor}
Jim Raynor was a Confederate marshal on Mar Sara at the time of the first zerg incursions on that world. He is now with Raynor's Raiders Inc.
\end{IEEEbiography}

>>>>

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/botopenings.pdf}
    \caption{Distribution of different openings performed by the different bots participating in the AIIDE 2011 competition. For each bot match-up, the colors show the proportion of times that the column bot used a particular opening against the row bot.}
    \label{fig:aiide2011-botopenings}
\end{figure*}

@@

However, there are many other problems for which this is not the case. For example, there is no current StarCraft bot that can come up with its own tactical moves, such as ``unit drops''. Some bots do drops, but only if this is hard-coded; no bot has the capability of reasoning about the current situation, synthesize a tactical move that involves a ``unit drop'', and determine that this move is the best one in the current situation. This is related to the lack of real-time adversarial planning techniques that scale up to the size required for RTS games.

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/botopenings2012.pdf}
    \caption{Distribution of different openings performed by the different bots participating in the AIIDE 2012 competition. For each bot match-up, the colors show the proportion of times that the column bot used a particular opening against the row bot.}
    \label{fig:aiide2012-botopenings}
\end{figure*}

Similarly, current bots do not exhibit adaptation to opponent strategies. Some switch between different build-orders, but do not fully adapt their strategy. No bot is capable of observing the opponent and autonomously synthesize a good plan from scratch to counter the opponent strategy. Figures \ref{fig:aiide2011-botopenings} and \ref{fig:aiide2012-botopenings} show evidence of this. We analyzed the replays from the 2011 and 2012 AIIDE competitions (shown in Figures \ref{fig:aiide2011-botopenings} and \ref{fig:aiide2012-botopenings} respectively). Specifically, we analyzed the way bots choose their openings depending on which other bot they are playing against. Given that there is no dominant strategy in StarCraft, and it is necessary to see what the opponent is doing in order to determine the best opening, we would expect bots to change their openings depending on which other bot they are playing (since each bot uses a different strategy, or set of strategies). Using clustering, we identified the most common openings in all the replays from the 2011 and 2012 competitions (each one shown with a different color in the figures). As the figures show, the top three ranked bots in the competition (Skynet, Aiur and UalbertaBot) do not change their strategy at all depending on their opponent. For example, the Skynet bot (both in 2011 and 2012), always uses the same opening (``two gates''), except when playing a Terran opponent, when it uses ``nony''. This reflects the trend that the performance of bots is still more dependent on carefully hand-crafted and non-adaptive behaviors, than on on-line decision making procedures. This is so, since most of the problems that need to be solved in order to implement such procedures are still open.

@@

%\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{jim.jpg}}]{Jim Raynor}
%Jim Raynor was a Confederate marshal on Mar Sara at the time of the first zerg incursions on that world. He is now with Raynor's Raiders Inc.
%\end{IEEEbiography}

%\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{figures/santi.jpg}}]{Santiago Onta\~{n}\'{o}n}
\begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 90 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
\end{IEEEbiographynophoto}
